Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

    We find that the stream is successfully recovered in both astrometric and
    photometric coordinates, with $\variable{output/mock/ncorrect_variable}\%$ stream
    stars being recovered with membership probability greater than $80\%$. The false
    positive rate (i.e., stars misidentified as stream members) for this test is
    found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
    this threshold.

>>>>

    We find that the stream is successfully recovered in both astrometric and
    photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ stream
    stars being recovered with membership probability greater than $80\%$. The false
    positive rate (i.e., stars misidentified as stream members) for this test is
    found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
    this threshold.
